\thispagestyle{empty}

\begin{center}

    \Large{\underline{\textbf{ACKNOWLEDGEMENT}}}\\

\end{center}

\vspace{1cm}

\noindent
I would like to express my sincere gratitude to \textbf{\gnameOne} and \textbf{\gnameTwo} for their
invaluable guidance and support throughout my project.
Their expertise has been instrumental in my success. I am truly grateful for their contributions
and the knowledge I have gained under their mentorship.

\vspace{0.5cm}

\noindent
I am also grateful to \textbf{\director}, Director, School of Sciences,
\textbf{Dr. K. N. Varalakshmi}, Director, Centre for Research in Pure \& Applied Sciences and
\textbf{Dr. S. A. Hariprasad}, Dean Academics, JAIN (Deemed-to-be
University) for providing us with this opportunity. I am thankful to
\textbf{\hod}, Head of the Department of Physics and Electronics and
\textbf{Dr. N. Shanthi}, Program-Head, M. Sc. Programme, for their constant
support and encouragement.

\vspace{0.5cm}

\noindent
I thank \textbf{Dr. Chenraj Roychand}, Chancellor, \textbf{Dr. N. Sundararajan},
Pro-Chancellor, \textbf{Dr. Jithendra Kumar Mishra}, Registrar and \textbf{Dr. Raj Singh}, Vice-Chancellor, JAIN (Deemed-to-be University), for
providing the required infrastructure and support without which this project would not have
been possible.

\vspace{0.5cm}

\noindent
I am grateful to all the faculty members, Mr. Arvind Krishnapur, Physics lab technician and Mr. Rajesh, Physics lab assistant for their kind support towards us.

\vspace{1.5cm}

\noindent
\begin{minipage}{0.5\textwidth}

    (\auth)

\end{minipage}%
\begin{minipage}{0.5\textwidth}
    \flushright

    \textbf{April, 2024\\
        Bengaluru}
\end{minipage}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "main"
%%% End:
